\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{natbib}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\begin{center}
    \LARGE{\textbf{Publication List}} \\
    \vspace{1em}
    \normalsize\textbf{Jung-hun Kim} \\
    \normalsize{junghunkim@snu.ac.kr}\\ 
    \normalsize{\url{https://sites.google.com/view/junghunkim}}
\end{center}

\section*{Publications}
\begin{enumerate}[label={[\arabic*]}]
    \item \textbf{[NeurIPS 2024]} {Queueing Matching Bandits with Preference Feedback.} \href{https://arxiv.org/pdf/2410.10098}{(link)} \\
    \underline{Jung-hun Kim}, Min-hwan Oh

    \item \textbf{[NeurIPS 2024]}
    {An Adaptive Approach for Infinitely Many-armed Bandits under Generalized Rotting Constraints.} \href{https://arxiv.org/pdf/2404.14202}{(link)}  \\
    \underline{Jung-hun Kim}, Milan Vojnovi{\'c}, Se-Young Yun

    \item \textbf{[AISTATS 2023]}
    {Contextual Linear Bandits under Noisy Features; Towards Bayesian Oracles.} \href{https://arxiv.org/pdf/1703.01347}{(link)}\\
    \underline{Jung-hun Kim}, Se-Young Yun, Minchan Jeong, Jun Hyun Nam, Jinwoo Shin, Richard Combes

    \item \textbf{[ICML 2022]}
    {Rotting Infinitely Many-armed Bandits.} \href{https://arxiv.org/pdf/2201.12975}{(link)} \\
    \underline{Jung-hun Kim}, Milan Vojnovi{\'c}, Se-Young Yun
    % \item \textbf{AISTATS 2023}: \href{https://proceedings.mlr.press/v206/kim23b/kim23b.pdf}{Contextual Linear Bandits under Noisy Features; Towards Bayesian Oracles.} \\
    % \underline{Jung-hun Kim}, Se-Young Yun, Minchan Jeong, Jun Hyun Nam, Jinwoo Shin, Richard Combes

    % \item \textbf{ICML 2022}: \href{https://proceedings.mlr.press/v162/kim22j/kim22j.pdf}{Rotting Infinitely Many-armed Bandits.} \\
    % \underline{Jung-hun Kim}, Milan Vojnovi{\'c}, Se-Young Yun

    \item \textbf{[IEEE Bigdata 2018]} {Research Hypothesis Generation Using Link Prediction in a Bipartite Graph.} \href{https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=8622645}{(link)} \\
    \underline{Jung-hun Kim}, Aviv Segev
\end{enumerate}

\section*{Working Papers}
\begin{itemize}
    \item (Submitted) {Dynamic Multi-product Selection and Pricing under Preference Feedback}; \underline{Jung-hun Kim}, Min-hwan Oh. \href{https://openreview.net/pdf?id=DOXnqYLCcd}{(link)}
    \item  (Submitted) {Stochastic Matching Bandits under Preference Feedback}; \underline{Jung-hun Kim}, Min-hwan Oh. \href{https://openreview.net/pdf?id=iKLSISIPH7}{(link)}
    \item (Submitted) {Scheduling Servers with Stochastic Bilinear Rewards}; \underline{Jung-hun Kim}, Milan Vojnovi{\'c}. \href{https://arxiv.org/pdf/2112.06362}{(link)}
\item{Adversarial Bandits against Arbitrary Strategies}; \underline{Jung-hun Kim} and Se-Young Yun. \href{https://arxiv.org/pdf/2205.14839}{(link)}
\end{itemize}
\end{document}
\entry{(Submitted) \href{https://openreview.net/pdf?id=DOXnqYLCcd}{Dynamic Multi-product Selection and Pricing under Preference Feedback}; \underline{Jung-hun Kim}, Min-hwan Oh}.
\entry{(Submitted) \href{https://openreview.net/pdf?id=iKLSISIPH7}{Stochastic Matching Bandit under Preference Feedback}; \underline{Jung-hun Kim}, Min-hwan Oh}
\entry{(Submitted) \href{https://arxiv.org/pdf/2112.06362}{Scheduling Servers with Stochastic Bilinear Rewards}; \underline{Jung-hun Kim} and Milan Vojnovi{\'c}.}}